Demonstration of matching route networks

### 2024-02-04 r/demo.qmd
Add length travelled and unevaluated python demo

dist = 20
angle = 40
rnet_merged = stplanr::rnet_merge(rnet_xp, rnet_yp, dist = dist, funs = funs, max_angle_diff = angle)

@@

>>>>

dist = 20
angle = 40
rnet_merged = stplanr::rnet_merge(rnet_xp, rnet_yp, dist = dist, funs = funs, max_angle_diff = angle)
# Explore distance travelled:
sum(rnet_merged$commute_fastest_bicycle_go_dutch * sf::st_length(rnet_merged$geometry))
# And for the complex network:
sum(rnet_yp$commute_fastest_bicycle_go_dutch * sf::st_length(rnet_yp$geometry))
tmap_mode("plot") # Set to view for interactive mode

@@

<!-- # In Python -->

```{python}
#| eval: false
#| echo: false
import geopandas as gpd
y = gpd.read_file("https://github.com/nptscot/rnetmatch/releases/download/intersection_road/intersection_example_complex.geojson")
y.plot()
# show it:
import matplotlib.pyplot as plt
plt.show()

x = gpd.read_file("https://github.com/nptscot/rnetmatch/releases/download/intersection_road/intersection_example_simple.geojson")
x.plot()
```
